Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-25 analysis/paper/paper.Rmd
clarify how predictors were treated

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 were used to predict responses with publishing journal, using the journals' abbreviation as the predictor (formula: response \~ abbreviation).
Models 3 and 4 were used to predict the two responses with year as the predictor (formula: response \~&nbsp;year) and the models included abbreviation and assignee as random effects (formula: list(\~1&nbsp;\|&nbsp;abbreviation,&nbsp;\~1&nbsp;\|&nbsp;assignee)).
Models 5 and 6 were used to predict the responses using IF_5year as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) and included assignee as random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
All models included the assigned article evaluator as a random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) to address inter-rater effects on scoring.

>>>>

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 were used to predict responses with publishing journal, using a factor, the journals' abbreviation, as the predictor (formula: response \~ abbreviation).
Models 3 and 4 were used to predict the two responses with a continuous value, year, as the predictor (formula: response \~&nbsp;year) and the models included abbreviation and assignee as random effects (formula: list(\~1&nbsp;\|&nbsp;abbreviation,&nbsp;\~1&nbsp;\|&nbsp;assignee)) to detect changes that occurred over the years in which the manuscripts were published that were included.
Models 5 and 6 were used to predict the responses using a continuous value, IF_5year, as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) and included assignee as random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
All models included the assigned article evaluator as a random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) to address inter-rater effects on scoring.
